Describe and Explore: Using feature-based time-series clustering to understand modern intensive longitudinal data (Working Title)

### 2022-11-27 methods-and-results.Rmd
:bug: tbl rotate

# Sample Descriptives Table --- wider version
allMlCor %>%
  t %>%
  kbl(.,
      format = "latex",
      caption = "Correlation Table and Descriptive Statistics",
      booktabs = TRUE,
      align = c("l", rep("c", ncol(.) - 1))) %>%
  kable_classic() %>%
  add_header_above(
    .,
    c(
      "",
      "Correlations" = ncol(allMlCor),
      "Descriptives" = nrow(allMlCor) - ncol(allMlCor)
    )
  ) %>%
  footnote(
    general = c(
      "Upper triangle: Between-person correlations;",
      "Lower triangle: Within-person correlations;",
      "*** p < .001, ** p < .01,  * p < .05"
    )
  ) %>%
  kable_styling(latex_options = "scale_down") %>%
  gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
  gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
  save_kable("Tables/descrWide.tex")

>>>>

# Sample Descriptives Table --- wider version
allMlCor %>%
  t %>%
  kbl(.,
      format = "latex",
      caption = "Correlation Table and Descriptive Statistics",
      booktabs = TRUE,
      align = c("l", rep("c", ncol(.) - 1))) %>%
  kable_classic() %>%
  add_header_above(
    .,
    c(
      "",
      "Correlations" = ncol(allMlCor),
      "Descriptives" = nrow(allMlCor) - ncol(allMlCor)
    )
  ) %>%
  footnote(
    general = c(
      "Upper triangle: Between-person correlations;",
      "Lower triangle: Within-person correlations;",
      "*** p < .001, ** p < .01,  * p < .05"
    )
  ) %>%
  kable_styling(latex_options = "scale_down") %>%
  gsub("\\begin{table}", "\\begin{sidewaystable}\n\\centering", ., fixed = TRUE) %>%
  gsub("\\end{table}", "\\end{sidewaystable}", ., fixed = TRUE) %>%
  save_kable("Tables/descrWide.tex")
